\bf The \texttt{forestecology} R package for modeling interspecies competition between trees

### 2021-02-15 etc/paper/forestecology.tex
Done "add spatial information" section

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    Define buffer region trees.
  \item
    Add spatial cross-validation block information.
  \end{enumerate}
\item
  Compute focal versus competitor tree information.
\item
  Fit model and make predictions.
\item
  Additionally: Evaluate model performance using spatial
  cross-validation.
\item
  Additionally: Evaluate the effect of competitor species identity using
  permutation tests.
\end{enumerate}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(lubridate)}
\KeywordTok{library}\NormalTok{(sf)}
\KeywordTok{library}\NormalTok{(forestecology)}
\end{Highlighting}
\end{Shaded}

@@

We now encode spatial information to the \texttt{growth\_df} data
frames. First, in order to control for study region edge effects, we add
``buffers'' to the periphery of the study region (cite Waller?). Our
model of interspecific competition relies on a spatial definition of who
the competitor trees are for focal trees of interest. Since certain
explanatory variables such as basal area are cumulative, we must ensure
that all trees being modeled are not biased to have different neighbor
structures. This is a particular concern for trees at the boundary of
study regions, which will not have the same number of neighbors as trees
in the internal part of the study region.

Second, our ultimate method for model assessment will rely on estimates
of model error as generated by cross-validation. Conventional
cross-validation schemes assign observations to folds by resampling
individual observations at random. However, underlying this scheme is an
assumption that the observations are independent. In the case of forest
census data, observations exhibit spatial autocorrelation, and thus this
dependence must be incorporated in our resampling scheme in spatial
cross-validation \citet{roberts_cross-validation_2017}
\citet{pohjankukka_estimating_2017} We will therefore associate portions
of the study region to spatial folds.

To these two ends, we define two constants, both of which are in the
same units as the \texttt{gx} and \texttt{gy} variables (most often
meters).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{comp_dist <-}\StringTok{ }\FloatTok{7.5}
\NormalTok{cv_fold_size <-}\StringTok{ }\DecValTok{100}
\end{Highlighting}
\end{Shaded}

The first constant is \texttt{comp\_dist} which defines the maximum
distance for a tree's competitive neighborhood. Trees within this
distance of each other are assumed to compete while those farther than
this distance apart do not. Put differently, all trees within
\texttt{comp\_dist} of a focal tree will be considered its competitors
(see below). Other studies have estimated the value of
\texttt{comp\_dist}; we use an average of estimated values
\citet{canham_neighborhood_2004}, \citet{uriarte_spatially_2004},
\citet{tatsumi2013}, \citet{canham_neighborhood_2006}.

Furthermore, \texttt{comp\_dist} will define the size of all buffers
considered, which will be encoded as a binary variable \texttt{buffer}
as computed by the \texttt{add\_buffer\_variable()} function. This
function takes as input the main \texttt{growth\_df} data frame, the
\texttt{size} of the buffer which we set as \texttt{comp\_dist}, and the
boundary of the study region encoded as a simple features polygon
\citet{pebesma_simple_2018}. DESCRIBE SF PACKAGE. In the Big Woods
example below we will use a pre-loaded simple features polygon while for
the SCBI example we present example code on how to manually construct
one.

The second constant is \texttt{cv\_fold\_size} which defines the length
and width of the spatial folds (note that for now the spatial folds are
restricted be squares). We will then use this constant to associate each
observed tree to one of \(k\) folds in the respective study region. In
the Big Woods example below we will use the \texttt{blockCV} R package
that has implemented spatial cross-validation while for the SCBI we will
do this manually \citet{valavi_blockcv_2019}

@@

First, we indicate which trees are part of the buffer. This necessitates
information about the study region boundary. In this case, we use a
\texttt{sf\_polygon} object \texttt{study\_region\_bw} which comes
pre-loaded in the \texttt{forestecology} packages. After loading
\texttt{study\_region\_bw}, we illustrate the results of the
\texttt{add\_buffer\_variable()} function in Figure
\ref{fig:bw-define-buffer}. Trees on the periphery denote with lighter
colors are part of the buffer and will not be considered as ``focal''
trees of interest going forward; they will only be considered as
competitor trees.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{data}\NormalTok{(study_region_bw)}

\NormalTok{growth_bw <-}\StringTok{ }\NormalTok{growth_bw }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{direction =} \StringTok{"in"}\NormalTok{, }\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_bw)}

\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_bw }\OperatorTok{%>%}\StringTok{ }\KeywordTok{sample_frac}\NormalTok{(}\FloatTok{0.2}\NormalTok{), }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{col =}\NormalTok{ buffer), }\DataTypeTok{size =} \FloatTok{0.5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=1\linewidth]{Figures/bw-define-buffer-1}

\caption{Buffer region for Big Woods study region.}\label{fig:bw-define-buffer}
\end{figure}

Second, we associate each tree to spatial cross validation folds. In
this case, we use the \texttt{spatialBlock()} function from the
\texttt{blockCV} package to define the spatial grid which

THIS IS A MESS. We use the \citet{valavi_blockcv_2019}, whose elements
will act as the folds in our leave-one-out (by ``one'' we mean ``one
grid block'') cross-validation scheme. The upshot here is we add
\texttt{foldID} to \texttt{growth\_df} which identifies which fold each
individual is in, and the creation of a \texttt{cv\_grid\_sf} object
which gives the geometry of the cross validation grid.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{76}\NormalTok{)}
\NormalTok{bw_spatialBlock <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}
  \DataTypeTok{speciesData =}\NormalTok{ growth_bw, }\DataTypeTok{theRange =}\NormalTok{ cv_fold_size, }\DataTypeTok{k =} \DecValTok{28}\NormalTok{, }\DataTypeTok{xOffset =} \FloatTok{0.5}\NormalTok{, }
  \DataTypeTok{yOffset =} \DecValTok{0}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Then add foldID to each tree

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth_bw <-}\StringTok{ }\NormalTok{growth_bw }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ bw_spatialBlock}\OperatorTok{$}\NormalTok{foldID)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Visualize grid. Why does fold 19 repeat?}
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ bw_spatialBlock}\OperatorTok{$}\NormalTok{blocks }\OperatorTok{%>%}\StringTok{ }\KeywordTok{st_as_sf}\NormalTok{()) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_bw }\OperatorTok{%>%}\StringTok{ }\KeywordTok{sample_frac}\NormalTok{(}\FloatTok{0.2}\NormalTok{), }
          \KeywordTok{aes}\NormalTok{(}\DataTypeTok{col =} \KeywordTok{factor}\NormalTok{(foldID)), }\DataTypeTok{size =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{show.legend =} \OtherTok{FALSE}\NormalTok{) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{geom_sf_text}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ bw_spatialBlock}\OperatorTok{$}\NormalTok{blocks }\OperatorTok{%>%}\StringTok{ }\KeywordTok{st_as_sf}\NormalTok{(), }
               \KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ folds))}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=1\linewidth]{Figures/bw-define-cv-folds-with-trees-1}

\caption{Inspect blocks closely.}\label{fig:bw-define-cv-folds-with-trees}
\end{figure}

Then remove empty folds

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{growth_bw <-}\StringTok{ }\NormalTok{growth_bw }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\NormalTok{foldID }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\DecValTok{19}\NormalTok{, }\DecValTok{23}\NormalTok{, }\DecValTok{21}\NormalTok{, }\DecValTok{17}\NormalTok{, }\DecValTok{8}\NormalTok{, }\DecValTok{19}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =} \KeywordTok{factor}\NormalTok{(foldID))}
\end{Highlighting}
\end{Shaded}

Separately, we save the spatial cross-validation grid as an
\texttt{sf\_polygon} object \texttt{blocks\_bw}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{blocks_bw <-}\StringTok{ }\NormalTok{bw_spatialBlock}\OperatorTok{$}\NormalTok{blocks }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{st_as_sf}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

First, we indicate which trees are part of the buffer. In this case
however we manually define the study region boundary based on the
subregion we defined in Section \ref{scbi-data} and create an
\texttt{sf\_polygon} object using the \texttt{sf\_polygon()} function
from the \texttt{sfheaders} package. Figure \ref{fig:scbi-define-buffer}
displays the resulting buffer trees.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}
  \DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{),}
  \DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{sf_polygon}\NormalTok{()}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{direction =} \StringTok{"in"}\NormalTok{, }\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_scbi)}

\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{col =}\NormalTok{ buffer), }\DataTypeTok{size =} \FloatTok{0.5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=0.5\linewidth]{Figures/scbi-define-buffer-1}

\caption{Buffer region for SCBI study region.}\label{fig:scbi-define-buffer}
\end{figure}

Second, we associate each tree to spatial cross validation folds. In
this case we manually define a spatial crossvaliation grid. Figure
\ref{fig:scbi-define-cv-folds} displays the resulting cross-validation
folds along with the buffer from Figure \ref{fig:scbi-define-buffer}.

Here we manually define the spatial cross-validation grid as an
\texttt{sf\_polygon} object \texttt{scbi\_cv\_grid}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}
  \KeywordTok{sf_polygon}\NormalTok{(fold1),}
  \KeywordTok{sf_polygon}\NormalTok{(fold2)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{SpatialBlock_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}
  \DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =} \DecValTok{2}\NormalTok{, }\DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi,}
  \DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}
\NormalTok{)}

\CommentTok{# Add foldID to each tree}
\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ SpatialBlock_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf_text}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ foldID, }\DataTypeTok{col =}\NormalTok{ buffer)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ blocks_scbi, }\DataTypeTok{fill =} \StringTok{"transparent"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=0.5\linewidth]{Figures/scbi-define-cv-folds-1}

\caption{Buffer region for SCBI study region.}\label{fig:scbi-define-cv-folds}
\end{figure}

@@

\hypertarget{viz-posterior-distributions}{%
\subsection{Visualize posterior
distributions}\label{viz-posterior-distributions}}

@@

\hypertarget{big-woods-4}{%
\subsubsection{Big Woods}\label{big-woods-4}}

@@

\hypertarget{scbi-4}{%
\subsubsection{SCBI}\label{scbi-4}}

>>>>

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    Define buffer region trees.
  \item
    Add spatial cross-validation block information.
  \end{enumerate}
\item
  Compute focal versus competitor tree information.
\item
  Fit model and make predictions.
\item
  Visualize model results.
\item
  Additionally: Evaluate model performance using spatial
  cross-validation.
\item
  Additionally: Evaluate the effect of competitor species identity using
  permutation tests.
\end{enumerate}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(lubridate)}
\KeywordTok{library}\NormalTok{(sf)}
\KeywordTok{library}\NormalTok{(forestecology)}
\KeywordTok{library}\NormalTok{(blockCV)}
\end{Highlighting}
\end{Shaded}

@@

The next step in our analysis sequence is to add spatial information to
our main \texttt{growth\_scbi} data frame. The first element of spatial
information we add is a ``buffer region'' to the periphery of the study
region. Since some of our model's explanatory variables such as
competitor basal area are cumulative, we must ensure that all trees
being modeled are not biased to have different neighbor structures. This
is of particular concern for trees at the boundary of study regions,
which will not have the same number of neighbors that act as competitors
as trees in the internal part of the study region. In order to account
for such edge effects only trees who are not part of this buffer region,
i.e.~are part of the interior of the study region, will have their
growths modeled \citet{waller_applied_2004}.

Our model of interspecific competition relies on a spatial definition of
who the competitor trees are for focal trees of interest: all trees
within a distance \texttt{comp\_dist} of a focal tree are considered its
competitors (assuming the same units as the \texttt{gx} and \texttt{gy}
location variables). In our case we set this value below at 7.5m, a
value informed by \citet{canham_neighborhood_2004}
\citet{uriarte_spatially_2004} \citet{canham_neighborhood_2006}. Using
this value along with a manually constructed \texttt{sf} object
representation of the study region's boundary, we apply the
\texttt{add\_buffer\_variable()} to our \texttt{growth\_scbi} data frame
to add a \texttt{buffer} boolean variable: all trees who have
\texttt{buffer} set to \texttt{FALSE} will be our focal trees whose
growths are modeled, whereas those with \texttt{buffer} set to
\texttt{TRUE} will only be considered as competitor trees whose growth
will not be modeled.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Define buffer region using competitive distance range}
\NormalTok{comp_dist <-}\StringTok{ }\FloatTok{7.5}

\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}
  \DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{),}
  \DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{sf_polygon}\NormalTok{()}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_scbi)}
\end{Highlighting}
\end{Shaded}

The second element of spatial information are blocks corresponding to
folds of a spatial cross-validation algorithm used to estimate model
error. Conventional cross-validation algorithms assign observations to
folds by randomly resampling individual observations. However,
underlying this algorithm is an assumption that the observations are
independent. In the case of forest census data, observations exhibit
spatial autocorrelation. This spatial dependence is incorporated into
the cross-validation algorithm by randomly resampling spatial blocks of
trees \citet{roberts_cross-validation_2017}
\citet{pohjankukka_estimating_2017}. We therefore associate each
observed tree to one of \(k\) spatial folds. In the example below, we
first manually define two folds that partition the study region as an
\texttt{sf} object. We then use the output of the
\texttt{spatialBlock()} function from the \texttt{blockCV} package to
associate each tree in \texttt{growth\_scbi} to the correct fold (saved
in the \texttt{foldID} variable) \citet{valavi_blockcv_2019}.
\textbackslash footnote\{In the Appendix we present an example where the
folds themselves are also created using the \texttt{spatialBlock()}
function given a specified \texttt{cv\_block\_size}.\}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Manually define spatial blocks to act as folds}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}
  \KeywordTok{sf_polygon}\NormalTok{(fold1),}
  \KeywordTok{sf_polygon}\NormalTok{(fold2)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{2}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{SpatialBlock_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}
  \DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =} \DecValTok{2}\NormalTok{, }\DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }
  \DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}
\NormalTok{)}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ SpatialBlock_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

Figure \ref{fig:scbi-spatial-information} illustrates the net effect of
adding these two elements of information to the \texttt{growth\_scbi}
data frame. The location of each tree is marked with an integer
indicating which fold it belongs to, where the folds are marked with
solid lines. The color of each digit indicates whether the tree is part
of the buffer region (and thus will only be considered as a competitor
tree in our model) or is part of the interior of the study region (and
thus is a focal tree whose growth is of modeled interest).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf_text}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{label =}\NormalTok{ foldID, }\DataTypeTok{col =}\NormalTok{ buffer), }\DataTypeTok{alpha =} \FloatTok{0.2}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ blocks_scbi, }\DataTypeTok{fill =} \StringTok{"transparent"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics[width=0.66\linewidth]{Figures/scbi-spatial-information-1}

\caption{Buffer region and cross-validation block information for SCBI data.}\label{fig:scbi-spatial-information}
\end{figure}

TODO: Do we talk about
\texttt{add\_buffer\_variable(direction\ =\ "out")} when each fold gets
its turn being the training data?

@@

@@

\hypertarget{viz-posterior-distributions}{%
\subsection{Visualize model results}\label{viz-posterior-distributions}}

@@

@@
